---
title: "ReLTER - Advanced use"
author: "Micha Silver"
date: "13/04/2022"
output:
    html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pkg_list <- c("sf", "terra", "ReLTER", "tmap")
lapply(pkg_list,require, character.only = TRUE)
tmap_options(check.and.fix = TRUE)
tmap_mode("view")
```

## Dependency on DEIMS-SDR

`ReLTER` relies on the data entered into DEIMS-SDR. However there are:

 - Multiple sites with similiar names
 - Missing information
 - Sites with no boundary polygon
 
#### First example, the Kiskun region of Hungary

```{r missing-data}
# Multiple sites in the KISKUN region of Hungary
kiskun <- get_ilter_generalinfo(country_name = "Hungary",
                              site_name = "KISKUN")
# How many sites?
print(paste("In Kiskun region: ", length(kiskun$title), "sites"))
(kiskun$title)
# Which site? Bugac-Bocsa
bugac_id <- kiskun[7,]$uri
bugac_details <- get_site_info(bugac_id,"Contacts")
(bugac_details$generalInfo.siteManager[[1]]['name'])
# Site manager is available

bugac_polygon <- get_site_info(bugac_id, "Boundaries")
str(bugac_polygon)
# No geometry
```
 - This site has the site manager's name
 - but no boundary polygon
 
#### Second example, Gran Paradiso in Italy

```{r similar-names}
paradiso <- get_ilter_generalinfo(country_name = "Italy",
                              site_name = "Gran Paradiso")
(paradiso$title)

# Choose the second
paradiso_id <- paradiso[2,]$uri
paradiso_details <- get_site_info(paradiso_id,"Contacts")
# Multiple names for metadata:
paradiso_details$generalInfo.metadataProvider[[1]]['name']
# No funding agency
paradiso_details$generalInfo.fundingAgency
```

 - This site has metadata providers
 - but no funding agency


## Acquiring Earth Observation data

Functions within ReLTER help to acquire certain Earth Observation datasets. The `get_site_ODS` function give `ReLTER` users access to the OpenDataScience Europe (ODS) archive (https://maps.opendatascience.eu/) with landcover, NDVI, natura2000 all at 30 meter pixel resolution. The Cropping to site boundaries is done in the cloud, and due to the Cloud Optimized Geotiff (COG) format, downloads are quite small. 

#### First example, Kis-Balaton site in Kiskun region, Hungary

```{r kis-balaton}
# Get DEIMS ID for Kis-Balaton site 
kis_balaton <- get_ilter_generalinfo(country_name = "Hungary",
                              site_name = "Kis-Balaton")
kb_id = kis_balaton$uri
kb_polygon = get_site_info(kb_id, "Boundaries")

# Now acquire landcover and NDVI from OSD
kb_landcover = get_site_ODS(kb_id, dataset = "landcover")
kb_ndvi_summer = get_site_ODS(kb_id, "ndvi_summer")

# Plot maps
tm_basemap() + 
  tm_shape(kb_polygon) +
  tm_borders(col = "purple") + 
  tm_shape(kb_ndvi_summer) +
  tm_raster(alpha=0.7, palette = "RdYlGn")

tm_basemap() + 
  tm_shape(kb_polygon) +
  tm_borders(col = "purple") + 
  tm_shape(kb_landcover) +
  tm_raster(alpha=0.7, palette = "Set1")
```

#### Second example, Companhia das Lezírias, Portugal

```{r companhia}
lezirias <- get_ilter_generalinfo(country_name = "Portugal",
                              site_name = "Companhia")
lezirias_id = lezirias$uri
lezirias_polygon = get_site_info(lezirias_id, "Boundaries")

# Now acquire spring NDVI from OSD
lezirias_ndvi_spring = get_site_ODS(lezirias_id, "ndvi_spring")

# Plot maps
tm_basemap() + 
  tm_shape(lezirias_polygon) +
  tm_borders(col = "purple") + 
  tm_shape(lezirias_ndvi_spring) +
  tm_raster(alpha=0.7, palette = "RdYlGn")

# The function outputs a raster. We can save to Geotiff for use in other GIS
class(lezirias_ndvi_spring)
writeRaster(x = lezirias_ndvi_spring,
            filename = "lezirias_ndvi_spring.tif",
            overwrite = TRUE)
```

 

## Additional plotting functions


```{r waffle}

```

