---
title: "ReLTER - Advanced use"
author: "Micha Silver"
date: "13/04/2022"
output:
    html_document:
    toc: true
    theme: united
---

[Back to TOC](index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pkg_list <- c("sf", "terra", "ReLTER", "tmap")
lapply(pkg_list,require, character.only = TRUE)
tmap_options(check.and.fix = TRUE)
tmap_mode("view")
```

## Dependency on DEIMS-SDR

`ReLTER` relies on the data entered into DEIMS-SDR. However there are:

 - Multiple sites with similiar names
 - Missing information
 - Sites with no boundary polygon
 
#### First example, the Kiskun region of Hungary

```{r missing-data}
# Multiple sites in the KISKUN region of Hungary
kiskun <- get_ilter_generalinfo(country_name = "Hungary",
                              site_name = "KISKUN")
# How many sites?
print(paste("In Kiskun region: ", length(kiskun$title), "sites"))
(kiskun$title)
# Which site? Bugac-Bocsa
bugac_id <- kiskun[7,]$uri
bugac_details <- get_site_info(bugac_id,"Contacts")
(bugac_details$generalInfo.siteManager[[1]]['name'])
# Site manager is available

bugac_polygon <- get_site_info(bugac_id, "Boundaries")
str(bugac_polygon)
# No geometry
```
 - This site has the site manager's name
 - but no boundary polygon
 
#### Second example, Gran Paradiso in Italy

```{r similar-names}
paradiso <- get_ilter_generalinfo(country_name = "Italy",
                              site_name = "Gran Paradiso")
(paradiso$title)

# Choose the second
paradiso_id <- paradiso[2,]$uri
paradiso_details <- get_site_info(paradiso_id,"Contacts")
# Multiple names for metadata:
paradiso_details$generalInfo.metadataProvider[[1]]['name']
# No funding agency
paradiso_details$generalInfo.fundingAgency
```

 - This site has metadata providers
 - but no funding agency


## Acquiring Earth Observation data

Functions within ReLTER help to acquire certain Earth Observation datasets. The `get_site_ODS` function give `ReLTER` users access to the OpenDataScience Europe (ODS) archive (https://maps.opendatascience.eu/) with landcover, NDVI, natura2000 all at 30 meter pixel resolution. The Cropping to site boundaries is done in the cloud, and due to the Cloud Optimized Geotiff (COG) format, downloads are quite small. 

#### First example, Kis-Balaton site in Kiskun region, Hungary

```{r kis-balaton}
# Get DEIMS ID for Kis-Balaton site 
kis_balaton <- get_ilter_generalinfo(country_name = "Hungary",
                              site_name = "Kis-Balaton")
kb_id = kis_balaton$uri
kb_polygon = get_site_info(kb_id, "Boundaries")

# Now acquire landcover and NDVI from OSD
kb_landcover = get_site_ODS(kb_id, dataset = "landcover")
kb_ndvi_summer = get_site_ODS(kb_id, "ndvi_summer")

# Plot maps
tm_basemap() + 
  tm_shape(kb_polygon) +
  tm_borders(col = "purple") + 
  tm_shape(kb_ndvi_summer) +
  tm_raster(alpha=0.7, palette = "RdYlGn")

tm_basemap() + 
  tm_shape(kb_polygon) +
  tm_borders(col = "purple") + 
  tm_shape(kb_landcover) +
  tm_raster(alpha=0.7, palette = "Set1")
```

#### Second example, Companhia das Lezírias, Portugal

```{r companhia}
lezirias <- get_ilter_generalinfo(country_name = "Portugal",
                              site_name = "Companhia")
lezirias_id = lezirias$uri
lezirias_polygon = get_site_info(lezirias_id, "Boundaries")

# Now acquire spring NDVI from OSD
lezirias_ndvi_spring = get_site_ODS(lezirias_id, "ndvi_spring")

# Plot maps
tm_basemap() + 
  tm_shape(lezirias_polygon) +
  tm_borders(col = "purple") + 
  tm_shape(lezirias_ndvi_spring) +
  tm_raster(alpha=0.7, palette = "RdYlGn")

# The function outputs a raster. We can save to Geotiff for use in other GIS
class(lezirias_ndvi_spring)
writeRaster(x = lezirias_ndvi_spring,
            filename = "lezirias_ndvi_spring.tif",
            overwrite = TRUE)
```

 

## Additional plotting functions


#### Environmental parameters

`ReLTER` has implemented some revealing visualizations of the various parameters collected at LTER sites. One visualization is the pie chart of environmental parameters.

In an example above the DEIMS ID of Kis Balaton (Kiskun LTER) was found. We'll use that site to show a pie chart of environmental variables collected in that site.

```{r pie-params}
produce_site_parameters_pie(kb_id)
```

Similarly, a "waffle" chart can be produced.

```{r waffle-params}
produce_site_parameters_waffle(kb_id)
```

#### Research topics, Related resources

List all research topics throughout an LTER network.

List related resources for an LTER network.

We demonstrate with the LTER network in Slovakia. Then filter for "Ecosystem" research.

```{r research-topics}
lter_slovakia_id <- "https://deims.org/networks/3d6a8d72-9f86-4082-ad56-a361b4cdc8a0"
slv_research_topics <- get_network_research_topics(lter_slovakia_id)
ecosystem_items <- grepl(pattern = "ecosystem",
                         slv_research_topics$researchTopicsLabel,
                         fixed = TRUE)
# Here is the filtered list
slv_research_topics[ecosystem_items,]

# List related resources
get_network_related_resources(lter_slovakia_id)
```

#### Show a map of sites in a network

This example uses the LTER network in Greece

The `produce_network_points_map()` function requires both DEIMS network ID and the three letter ISO code for the country to be mapped.

```{r network-map}
lter_greece_id = "https://deims.org/networks/83453a6c-792d-4549-9dbb-c17ced2e0cc3"
produce_network_points_map(lter_greece_id, "GRC")
```


[Back to TOC](index.html)
