---
title: "`R` and RStudio Intro"
author: "Micha Silver"
date: "13/04/2022"
output:
  html_document:
    toc: true
    theme: united
---

[Back to TOC](index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Beginning with Rstudio and git

#### Some online resources
 - R for Data Science: https://r4ds.had.co.nz/index.html 
 - Geocomputation with R: https://geocompr.robinlovelace.net/
 - Rseek: https://rseek.org/
 

#### Start a new package **based on a git repo**.

Encourages collaboration "out of the box".

Basics of git:

  - https://git-scm.com/book/en/v2/Git-Basics-Getting-a-Git-Repository
  - https://r-bio.github.io/intro-git-rstudio/

#### RStudio hints

  - Always work in an R project
  - Do **not** `setwd()`
  - Do **not save workspace** to `.Rdata`
  - Use Control+Shift+F10 often
 
#### Markdown versus `R` script
 - Code is the same
 - RMarkdown adds formatted text and outputs
 - Perfect for reports and ... demos

  
## Where to get `R` packages
 
 - CRAN: https://cran.r-project.org/
 - BioConductor: https://www.bioconductor.org/install/
 - Packages developed on github, i.e. `ReLTER`
 
```{r packages, message=FALSE}
# Install some standard spatial packages from CRAN
if (!require("sf", quietly = TRUE))
  install.packages(c("sf", "terra"))

# package from Bioconductor
if (!require("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install()
BiocManager::install("EBImage")

# Install development package from github
if (!require("remotes", quietly = TRUE))
  install.packages("remotes")

if (!require("ReLTER", quietly = TRUE))
  remotes::install_github("oggioniale/ReLTER")
``` 
## Loading packages

After installing, we need to load the packages into this `R` session.

```{r loading}
# Convenient way to load list of packages
pkg_list <- c("sf", "terra", "ReLTER", "tmap")
lapply(pkg_list,require, character.only = TRUE)
```

[Back to TOC](index.html)


