---
title: "ReLTER - Advanced use"
author: "Alessandro Oggioni and Micha Silver"
date: "13/04/2022"
output:
  ioslides_presentation:
    smaller: true
    logo: figures/eLTER_logo_small.png
    css: styles.css
---

```{r adv-setup, include=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r adv-packages, message=FALSE, warning=FALSE, include=FALSE}
pkg_list <- c("sf", "terra", "ReLTER", "tmap")
lapply(pkg_list, require, character.only = TRUE)
tmap_options(check.and.fix = TRUE)
tmap_mode("view")
```

## Dependency on DEIMS-SDR

`ReLTER` relies on the data entered into DEIMS-SDR. However sometimes there are:

 - Multiple sites with similar names
 - Missing information
 - Sites with no boundary polygon
 
#### First example, the Kiskun region of Hungary

Query for Site Manager

```{r adv-missing}
# Multiple sites in the KISKUN region of Hungary
kiskun <- ReLTER::get_ilter_generalinfo(country_name = "Hungary",
                              site_name = "KISKUN")
# How many sites?
print(paste("In Kiskun region: ", length(kiskun$title), "sites"))
```

----

```{r adv-missing2}
(kiskun$title)
# Which site? Bugac-Bocsa
bugac_id <- kiskun[7,]$uri
bugac_details <- ReLTER::get_site_info(bugac_id,"Contacts")
(bugac_details$generalInfo.siteManager[[1]]['name'])
```

----

Now query for boundary

```{r adv-missing-boundary}
bugac_polygon <- ReLTER::get_site_info(bugac_id, "Boundaries")
str(bugac_polygon)
# No geometry
```

 - This site has the site manager's name
 - but no boundary polygon
 
----

#### Second example, Gran Paradiso in Italy

```{r adv-paradiso}
paradiso <- ReLTER::get_ilter_generalinfo(country_name = "Italy",
                              site_name = "Gran Paradiso")
(paradiso$title)

# Choose the second
paradiso_id <- paradiso[2,]$uri
paradiso_details <- ReLTER::get_site_info(paradiso_id, "Contacts")
# Multiple names for metadata:
paradiso_details$generalInfo.metadataProvider[[1]]['name']
```

----

```{r adv-paradiso-info}
# But what about funding agency
paradiso_details$generalInfo.fundingAgency
```

 - This site has metadata providers
 - but no funding agency


## Acquiring Earth Observation data

Functions within `ReLTER` help to acquire certain Earth Observation datasets.

The `get_site_ODS()` function offers to `ReLTER` users access to the OpenDataScience Europe (ODS) archive (https://maps.opendatascience.eu/) with landcover, NDVI, natura2000, Corine landcover, and OSM features, all at 30 meter pixel resolution. Cropping to site boundaries is done in the cloud, and due to the Cloud Optimized Geotiff (COG) format, downloads are quite small. 

----

#### First example, Kis-Balaton site in Kiskun region, Hungary

```{r adv-balaton-ods}
# Get DEIMS ID for Kis-Balaton site 
kis_balaton <- ReLTER::get_ilter_generalinfo(country_name = "Hungary",
                              site_name = "Kis-Balaton")
kb_id = kis_balaton$uri
kb_polygon = ReLTER::get_site_info(kb_id, "Boundaries")

# Now acquire landcover and NDVI from ODS
kb_landcover = ReLTER::get_site_ODS(kb_id, dataset = "landcover")
kb_ndvi_summer = ReLTER::get_site_ODS(kb_id, "ndvi_summer")
```

----

```{r adv-balaton-plot}
# Plot maps
tm_basemap("OpenStreetMap.Mapnik") + 
  tm_shape(kb_polygon) +
  tm_borders(col = "purple") + 
  tm_shape(kb_ndvi_summer) +
  tm_raster(alpha=0.7, palette = "RdYlGn")
```
----
 
```{r adv-balaton-plot2}
tm_basemap("OpenStreetMap.Mapnik") + 
  tm_shape(kb_polygon) +
  tm_borders(col = "purple") + 
  tm_shape(kb_landcover) +
  tm_raster(alpha=0.7, palette = "Set1")
```

----

#### Second example, Companhia das Lezírias, Portugal

```{r adv-companhia}
lezirias <- ReLTER::get_ilter_generalinfo(country_name = "Portugal",
                              site_name = "Companhia")
lezirias_id = lezirias$uri
lezirias_polygon = ReLTER::get_site_info(lezirias_id, "Boundaries")

# Now acquire spring NDVI from OSD
lezirias_ndvi_spring = ReLTER::get_site_ODS(lezirias_id, "ndvi_spring")
```

----

```{r adv-companhia-plot}
# Plot maps
tm_basemap("OpenStreetMap.Mapnik") + 
  tm_shape(lezirias_polygon) +
  tm_borders(col = "purple") + 
  tm_shape(lezirias_ndvi_spring) +
  tm_raster(alpha=0.7, palette = "RdYlGn")
```

----

The function outputs a raster. We can save to Geotiff for use in other GIS

```{r adv-save}
class(lezirias_ndvi_spring)
writeRaster(x = lezirias_ndvi_spring,
            filename = "lezirias_ndvi_spring.tif",
            overwrite = TRUE)
```

## Acquiring biodiversity data

Functions within `ReLTER` help to acquire certain third parties biodiversity datasets. The `get_site_speciesOccurrences` function^1^, offers to `ReLTER` users access to the occurrence records from [GBIF](https://www.gbif.org) (via [`rgbif` R package](https://docs.ropensci.org/rgbif/)), [iNaturalist](https://www.inaturalist.org/) and [OBIS](https://obis.org/) carried out within the boundaries of the site.

Coauthor of these functions are Martina Zilioli and Paolo Tagliolato.

<font size="2">^1^ `get_site_speciesOccurrences`, `map_occ_gbif2elter` and `save_occ_eLTER_reporting_Archive` currently are delivered only with dev__withImprovements branch of `ReLTER`</font> 

----

#### First example, the Gulf Of Venice (GOV)

```{r adv-GOF, warning=FALSE, message=FALSE, eval=FALSE}
DEIMS.iD of eLTER site Gulf Of Venice (GOV)
GOVid <- "https://deims.org/758087d7-231f-4f07-bd7e-6922e0c283fd"
resGOV <- ReLTER::get_site_speciesOccurrences(
  deimsid = GOVid, list_DS = "obis", show_map = TRUE, limit = 10)
```

<iframe src="./other/occurrences_GOV.html" height="360" width="650" style="border: 1px solid #464646;"></iframe>

----

#### Second example, the Saldur River Catchment

```{r Saldur, warning=FALSE, message=FALSE, eval=FALSE}
# DEIMS.iD of eLTER the Saldur River Catchment site 
saldur_id <- "https://deims.org/97ff6180-e5d1-45f2-a559-8a7872eb26b1"
occ_SRC <- ReLTER::get_site_speciesOccurrences(
  deimsid = saldur_id, list_DS = c("gbif", "inat"), show_map = TRUE, limit = 100)
```

<iframe src="./other/occurrences_saldur.html" height="360" width="650" style="border: 1px solid #464646;"></iframe>

----

#### Trasform this data into eLTER data template

Fields mapping among the three data source schemas (i.e., GBIF, iNaturalist, OBIS) and the eLTER data-reporting template (Peterseil et al., 2021) was carried out so as to design `ReLTER` functions: `map_occ_gbif2elter` and `save_occ_eLTER_reporting_Archive`.

Below an example of iNaturalist export data, for the Saldur River Catchment site.


```{r export, warning=FALSE, message=FALSE, eval=FALSE}
library(dplyr)
saldurid <- "https://deims.org/97ff6180-e5d1-45f2-a559-8a7872eb26b1"
resSaldur <- ReLTER::get_site_speciesOccurrences(
  deimsid = saldurid, list_DS = c("gbif", "inat"), show_map = FALSE, limit = 20,
  exclude_inat_from_gbif = TRUE)
# iNaturalist
tblSaldur_inat <- tibble::as_tibble(resSaldur$inat)
outInat <- tblSaldur_inat %>%
  ReLTER::map_occ_inat2elter(deimsid = saldurid)
ReLTER::save_occ_eLTER_reporting_Archive(outInat)
```

The eLTER useful archive created is:

* biodiv_occurrence_site_97ff6180-e5d1-45f2-a559-8a7872eb26b1_inat.zip

## Additional plotting functions

#### Environmental parameters

`ReLTER` has implemented some revealing visualizations of the various parameters collected at LTER sites. One visualization is the pie chart of environmental parameters.

----

In an example above the DEIMS ID of Kis Balaton (Kiskun LTER) was found. We'll use that site to show a pie chart of environmental variables collected in that site.

```{r adv-pie-params, warning=FALSE, message=FALSE}
ReLTER::produce_site_parameters_pie(kb_id)
```

----

Similarly, a "waffle" chart can be produced.

```{r adv-waffle-params, warning=FALSE, message=FALSE}
ReLTER::produce_site_parameters_waffle(kb_id)
```

----

<!-- #### Research topics, Related resources -->

<!-- List all research topics throughout an LTER network. -->

<!-- List related resources for an LTER network. -->

<!-- We demonstrate with the LTER network in Slovakia. Then filter for "Ecosystem" research. -->

<!-- ```{r research-topics} -->
<!-- lter_slovakia_id <- "https://deims.org/networks/3d6a8d72-9f86-4082-ad56-a361b4cdc8a0" -->
<!-- slv_research_topics <- get_network_research_topics(lter_slovakia_id) -->
<!-- ecosystem_items <- grepl(pattern = "ecosystem", -->
<!--                          slv_research_topics$researchTopicsLabel, -->
<!--                          fixed = TRUE) -->
<!-- # Here is the filtered list -->
<!-- slv_research_topics[ecosystem_items,] -->
<!-- ``` -->

<!-- ---- -->

<!-- #### List related resources -->
<!-- ```{r related-resources} -->
<!-- get_network_related_resources(lter_slovakia_id) -->
<!-- ``` -->

<!-- ---- -->

#### Show a chaining of several functions

This example uses the LTER network in Greece. Call the `produce_network_points_map()` function (requires both DEIMS network ID and the three letter ISO code for the country to be mapped) to get all sites in a country.

```{r adv-greece-network}
lter_greece_id = "https://deims.org/networks/83453a6c-792d-4549-9dbb-c17ced2e0cc3"
lter_greece <- ReLTER::produce_network_points_map(lter_greece_id, "GRC")
grc <- readRDS("gadm36_GRC_0_sp.rds")  # available from `produce_network_points_map()
```

----

```{r adv-greece-plot}
tm_basemap("OpenStreetMap.Mapnik") + 
  tm_shape(lter_greece) + 
  tm_dots(col = "blue", size=0.08) +
  tm_shape(grc) + 
  tm_borders(col = "purple", lwd=2) +
  tm_grid(alpha = 0.4) +
  tm_scale_bar(position = c("right", "bottom"))
```
