---
title: "Introducing ReLTER"
author: "Micha Silver"
date: "13/04/2022"
output:
  html_document:
    toc: true
    theme: united
---

[Back to TOC](index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Convenient way to load list of packages
pkg_list <- c("sf", "terra", "ReLTER", "tmap")
lapply(pkg_list,require, character.only = TRUE)
tmap_options(check.and.fix = TRUE)
tmap_mode("view")
```

## What is ReLTER

```{r about}
library(ReLTER)
maintainer("ReLTER")
citation("ReLTER")
```

## Basic functions

```{r functions}
ls("package:ReLTER")
```

#### Categories

  - site specific functions
  - network functions
  - metadata functions
  - taxonomy functions
 
## Examples

Search for DEIMS ID for a particular site. The function `get_ilter_generalinfo` allows to search by country name and site name.

```{r example1}
# Hohe Tauern National Park
hohe = get_ilter_generalinfo(country_name = "Austria",
                              site_name = "Hohe Tauern")
(hohe_id = hohe$uri)
```

#### Plot a basic map of that site. We use the `tmap` package for viewing maps.

```{r plot-site}
hohe_polygon <- get_site_info(hohe_id, category = "Boundaries")
tm_basemap() + 
  tm_shape(hohe_polygon) +
  tm_fill(col = "blue", alpha = 0.3)
```

#### Retrieve metadata about a site. 

```{r example2}
#In this example Loch Kinord in Scotland. 

loch_kinord <- get_ilter_generalinfo(country_name = "United K",
                              site_name = "Loch Kinord")
(loch_kinord_id = loch_kinord$uri)
loch_kinord_details <- get_site_info(loch_kinord_id,
                                 c("Contacts", "EnvCharacts", "Parameters"))

print(paste("Site manager:",
            loch_kinord_details$generalInfo.siteManager[[1]]['name'],
            loch_kinord_details$generalInfo.siteManager[[1]]['email']))
print("Metadata contact:")
(loch_kinord_details$generalInfo.metadataProvider[[1]]['name'])
print(paste("Average air temperature:",
            loch_kinord_details$envCharacteristics.airTemperature.avg))
print(paste("Annual precipitation:",
            loch_kinord_details$envCharacteristics.precipitation.annual))
print(paste("GeoBonBiome:",
            loch_kinord_details$envCharacteristics.geoBonBiome[[1]]))
print("Parameters:")
(loch_kinord_details$parameter[[1]]['parameterLabel'])

```

#### Query a network, The LTER network in Slovakia

```{r example3}
lter_slovakia_id = "https://deims.org/networks/3d6a8d72-9f86-4082-ad56-a361b4cdc8a0"

network_research_topics <- get_network_research_topics(lter_slovakia_id)
head(network_research_topics$researchTopicsLabel, 20)
network_sites <- get_network_sites(lter_slovakia_id)
network_sites$title
```

#### Show map of network

```{r network-map}
lter_slovakia <- produce_network_points_map(lter_slovakia_id, "SVK")
# The country border is available after running produce_network_points_map()
svk <- readRDS("gadm36_SVK_0_sp.rds")
tm_basemap() + 
  tm_shape(lter_slovakia) + 
  tm_dots(col = "blue", size=0.04) +
  tm_shape(svk) + 
  tm_borders(col = "purple") +
  tm_grid(alpha = 0.4) +
  tm_scale_bar(position = c("right", "bottom"))
```

[Back to TOC](index.html)
