---
title: "Introducing `ReLTER`"
subtitle: "Mallorca eLTER-Plus and PPP conference"
author: "Alessandro Oggioni and Micha Silver"
date: "12/05/2022"
output:
  ioslides_presentation:
    smaller: true
    logo: figures/eLTER_logo_small.png
    css: styles.css
    widescreen: true
---

```{r relter-setup, include=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Convenient way to load list of packages
pkg_list <- c("sf", "terra", "ReLTER", "tmap", "knitr", "glue")
lapply(pkg_list, require, character.only = TRUE)
tmap_options(check.and.fix = TRUE)
tmap_mode("view")
```

## What is `ReLTER`

`ReLTER` is an R package that: **provides access to [DEIMS-SDR](https://deims.org/)**, allows **interact** with software implemented by eLTER Research Infrastructure (RI) and **improves the data/information shared** by them.

`ReLTER` **is born within eLTER-Plus H2020 project** and it shall definitely follow the progress of ([eLTER RI](https://elter-ri.eu/)).

`ReLTER` passed the peer review of [ROpenSci](https://ropensci.org/packages/all/), the biggest R community for open tools and open science.

<iframe src="https://ropensci.r-universe.dev/ui#package:ReLTER" scrolling= "yes"></iframe>

## How to pronounce `ReLTER`

<font size="8">riːˈɛl-tiː-iː-ɑː</font>

```{r setup, include = FALSE}
html_tag_audio <- function(file, type = c("wav")) {
  type <- match.arg(type)
  htmltools::tags$audio(
    controls = "",
    htmltools::tags$source(
      src = file,
      type = glue::glue("audio/{type}", type = type)
    )
  )
}
```

#### Audio

`r html_tag_audio("sounds/ReLTER.wav")`

## Documentation of `ReLTER`

Visit the `ReLTER` website at
[docs.ropensci.org/ReLTER/](https://docs.ropensci.org/ReLTER/) for
further documentation, examples, and installation of the package.

<iframe src="https://docs.ropensci.org/ReLTER/" scrolling= "yes"></iframe>

## How to collaborate with `ReLTER`

There are several ways you can contribute to this project.

### Ask a question ⁉️, Report a bug 🐛 or Propose an idea 💡

Using `ReLTER` and got stuck? Take a look at the [documentation](https://docs.ropensci.org/ReLTER/) and [issue list](https://github.com/ropensci/ReLTER/issues)

### Contribute code 📝

Care to fix bugs or implement new functionality for `ReLTER`? Awesome! 👏

Please ask to us!!


## How to cite `ReLTER`

```{r relter-citation, message=FALSE, results='hide'}
citation("ReLTER")

## To cite the 'ReLTER' package in publications use:
##
##   Alessandro Oggioni, Micha Silver, Luigi Ranghetti & Paolo Tagliolato.
##   (2021). oggioniale/ReLTER: ReLTER v1.1.0 (1.1.0). Zenodo.
##   https://doi.org/10.5281/zenodo.5576813
##
## A BibTeX entry for LaTeX users is
##
##   @software{alessandro_oggioni_2021_5576813,
##   author       = {Alessandro Oggioni and Micha Silver and
##                   Luigi Ranghetti and Paolo Tagliolato},
##   title        = {ropensci/ReLTER: ReLTER v1.1.0},
##   year         = 2022,
##   publisher    = {Zenodo},
##   version      = {1.1.0},
##   doi          = {10.5281/zenodo.5576813},
##   url          = {https://doi.org/10.5281/zenodo.5576813}
## }
```

## Examples:

#### Search for DEIMS ID for a site (1/3)

The function `get_ilter_generalinfo()` allows to search by country name and site name.

Then `get_site_info()` obtains various metadata about a chosen site.

#### For this example, the Doñana LTSER Platform in Spain

```{r relter-donana}
donana <- ReLTER::get_ilter_generalinfo(country_name = "Spain",
                              site_name = "Doñana")
donana_id = donana$uri
```

----

Plot a basic map of that site. We use the `tmap` package for viewing maps.

```{r relter-plot-donana}
donana_id <- "https://deims.org/bcbc866c-3f4f-47a8-bbbc-0a93df6de7b2"
donana_polygon <- ReLTER::get_site_info(donana_id, category = "Boundaries")
tm_basemap("OpenStreetMap.Mapnik") +
  tm_shape(donana_polygon) +
  tm_fill(col = "blue", alpha = 0.3)
```

----

#### Retrieve metadata about a particular site (2/3)

This example retrieves metadata from Lock Kinord in Scotland.

```{r relter-kinord-info}
loch_kinord_id <- "https://deims.org/9fa171d2-5a24-40d3-9c06-b3f9e9d0f270"
loch_kinord_details <- ReLTER::get_site_info(loch_kinord_id,
                                 c("Contacts", "EnvCharacts", "Parameters"))

print(paste("Site manager:",
            loch_kinord_details$generalInfo.siteManager[[1]]['name'],
            loch_kinord_details$generalInfo.siteManager[[1]]['email']))
```

----

```{r relter-kinord-metadata}
# Metadata contact:
(loch_kinord_details$generalInfo.metadataProvider[[1]]['name'])

glue("Average air temperature: ",
            loch_kinord_details$envCharacteristics.airTemperature.avg)
glue("Annual precipitation: ",
            loch_kinord_details$envCharacteristics.precipitation.annual)
```

----

```{r relter-kinord-geobonbiome}
glue("GeoBonBiome:",
            loch_kinord_details$envCharacteristics.geoBonBiome[[1]])
# Parameters:
kable(head(loch_kinord_details$parameter[[1]], 12))
```

----

#### Related resources (3/3)

The `get_site_info` function provides a list of related resources (e.g. datasets) shared by a site (e.g. Lake Maggiore)

```{r rlter-related_resources}
tSiteRelatedResources <- ReLTER::get_site_info(
  deimsid = "https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe",
  category = "RelateRes"
)
kable(tSiteRelatedResources$relatedResources[[1]])
```

## More info ...

Join to SE18!!

<iframe src="https://docs.google.com/document/d/1omDa3lDHnNP23T0amVv_oeEuBL7Hl73e/edit#heading=h.gjdgxs" scrolling= "yes"></iframe>